Stat 400 Project

### 2021-11-18 Stat 400 proj.Rmd
crucial distance
created the starting_vals function, and started working on a basic simulation function

```{r}
incubation_time <- rgamma(5, 6, (2/3))
```

>>>>

```{r}
library(tidyverse)

incubation_time <- rgamma(5, 6, (2/3))
crucial_distance <- rexp(5, 1/8)

#starter subjects vector
subjects <- rep('S', 100)

#area grid
grid_x <- 50
grid_y <- 50

#starting positions
start_x <- rep(NA, length(subjects))
start_y <- rep(NA, length(subjects))

for(i in 1:length(subjects)){
  start_x[i] <- runif(n=1, min=0, max=grid_x)
  start_y[i] <- runif(n=1, min=0, max=grid_y)
}

#plot the starting positions
ggplot() +
  geom_point(aes(x=start_x, y=start_y))

#Create df of values for infection status, x coordinate, and y coordinate
df <- as.data.frame(cbind(subjects, start_x, start_y))
df$subjects <- as.factor(df$subjects)

#create starting positions function
starting_vals <- function(num_subjects, x_dim, y_dim){

  start_x <- rep(NA, length(subjects))
  start_y <- rep(NA, length(subjects))

  for(i in 1:num_subjects){
  start_x[i] <- runif(n=1, min=0, max=grid_x)
  start_y[i] <- runif(n=1, min=0, max=grid_y)
  }

  return(cbind(start_x, start_y))
}

#simulation function
simulator <- function(days, num_subjects, x_dim, y_dim){
  subjects <- rep('S', num_subjects)
  start_coords <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim)
  starter_data <- cbind(subjects, start_coords)

}

```
